### 2013-06-04 doc/pgas13/evaluation.tex
Add Hash{Set,Map} plots.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{data/plots/queue_perf.pdf}
  \caption{Queue performance.}
  \label{fig:queue}
  \end{subfigure}%
  \hspace{0.05\textwidth}
  % ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{data/plots/stack_perf.pdf}
  \caption{Stack performance.}
  \label{fig:stack}
  \end{subfigure}
  \caption{Raw performance of global data structures.}\label{fig:datastructs}
\end{figure*}

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{data/plots/stack_perf.pdf}
  \caption{Stack performance.}
  \label{fig:stack}
  \end{subfigure}%
  \hspace{0.05\textwidth}
  % ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{data/plots/queue_perf.pdf}
  \caption{Queue performance.}
  \label{fig:queue}
  \end{subfigure}

  \begin{subfigure}[b]{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{data/plots/hashset_perf.pdf}
  \caption{GlobalHashSet performance.}
  \label{fig:hashset}
  \end{subfigure}
  %
  \hspace{0.05\textwidth}
  %
  \begin{subfigure}[b]{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{data/plots/hashmap_perf.pdf}
  \caption{GlobalHashMap performance.}
  \label{fig:hashmap}
  \end{subfigure}%
  %
  \caption{Raw performance of global data structures.
    \TODO{describe results.}
    \TODO{either all with error bars or none.}
  }\label{fig:datastructs}
\end{figure*}
